### 2016-07-22 version0.0/appendixa.tex
Submitted version

\chapter{SFR from H$\alpha$ Plus 24 \um: Procedure and Result}
\pagestyle{plain}
\label{app:halpha}
\myappendices
As mentioned in Section~\ref{sec: data_sfl}, we used the \halpha\ data from the Nearby Galaxies Survey~\citep{Massey07} to create one of our SFR maps. These data cover 10 overlapping fields across the disk of M31 in broad and narrow bands and were observed between August 2000 and September 2002; we obtained them  from the NOAO Science Archive. Making a spatially resolved SFR map of M31 using \halpha\ emission requires removal of background and stellar emission in each field, masking out foreground stars and saturated regions, creating a mosaic of \halpha\ continuum-subtracted images, and finally correcting for the flux contribution to the \halpha\ filter from the \nii\ 6583~\AA\ line.

>>>>

\chapter{SFR from H$\alpha$ Plus 24~$\mu$m: Procedure and Result}
\pagestyle{plain}
\label{app:halpha}
\myappendices

As mentioned in Section~\ref{sec: data_sfl}, we used the \halpha\ data from the Nearby Galaxies Survey~\citep{Massey07} to create one of our SFR maps. These data cover 10 overlapping fields across the disk of M31 in broad and narrow bands and were observed between August 2000 and September 2002; we obtained them  from the NOAO Science Archive. Making a spatially resolved SFR map of M31 using \halpha\ emission requires removal of background and stellar emission in each field, masking out foreground stars and saturated regions, creating a mosaic of \halpha\ continuum-subtracted images, and finally correcting for the flux contribution to the \halpha\ filter from the \nii\ 6583~\AA\ line.

### 2016-07-22 version0.0/asli.tex
Submitted version

\newcommand{\makeacknowlege} { 1) Pauline
2) Els, Sophia, Hossein,
3)I would like to thank all my Friends in Western. Neven, dave, Matt, parshati, sina, zahra, fereshteh, aycha, maryam(s) , Laura, Taylor, dimuthu, Sham, ghazal, pubu, robin, Hoori, Javad, ali, shanon, Mohad, Boshra
4) bacheha
5) western ppl; Jodi, Brian, Henry, Phin,...
6) Mohad, shahin, pejman, pouria, masood,babak
7) fako famil
}
\newcommand{\makededications} {

@@

\vfill
\textbf{Keywords:} Nearby galaxies: M31, M101, Star formation rate, stellar mass, ISM, data mining
\newpage
\tableofcontents\newpage
\newpage
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures
\newpage
\addcontentsline{toc}{chapter}{List of Tables}
\listoftables\newpage
% \addcontentsline{toc}{chapter}{List of Appendices}
% \listofmyappendices\newpage
%\addcontentsline{toc}{chapter}{List of Abbreviations, Symbols, and Nomenclature}
%\large List of Abbreviations, Symbols, and Nomenclature \normalsize
%\newpage
\end{preliminary}
%% End of the preliminary sections: reset page style and numbering.

>>>>

\newcommand{\makeacknowlege} { 
This is the first or second page to be read of this thesis, but the last one written.
I will try to thank all the people that helped me during studies, and gave me courage to continuing this process.
My most gratitude goes to my awesome supervisor, Prof. Pauline Barmby, for all the support during the last four years;
the amount I've learned from her, her knowledge and superb physical intuition is incalculable.
She is truly one of the best supervisors in the world.

I also would like to thank all my collaborators Prof. E. Peeters, Dr. S. Lianue, and Dr. H. Teimoorinia for not only helping me on moving my projects forward, but also for teaching me how a good scientist work.
Thank you to Dr. D. Stock and Dr. M. Azimlu for all your useful comments.

I would like to thank all my fellow graduate students in Western University: Alex, Aycha, Beth, Boshra, Dimuthu, Fereshteh, Ghazal, Hoori, Javad, Laura, Maryam(s), Matt, Neven, Parshati, Pubu, Robin, Sina, Sham, Taylor and Zahra.
You guys are amazing; you helped me whenever I needed, and I had so much fun hanging out with you.
Thank you Western Physics and Astronomy department staff, especially Clara Buma, Brian Davis, Jodi Guthrie, Henry Leparskas, and Phin Perquin for helping me with the problems an international student can have.

My dearest friend, Nazanin P., my thanks goes to you and your family.
During our 18 years of friendship you always encouraged me and was there for me whenever I needed anything.
Your help when I was applying for graduate school and when I moved to Canada, was priceless. You are the loveliest family in the world.
Matin, Sogol, Mercedeh, Alireza, Farhad and Ardeshir thank you for always finding a way to remind me my dreams when I was too busy or too tiered to continue.

Last but not least, I want to thank my family.
My father, who thought me to learn from my mistakes and not to repeat them.
My mother, who is always available to talk to and make me feel better.
Setareh, who I hope she knows that I am here in this stage of my life all because of her believing in me.
Seti, "aroosakam", my little secret-keeper, whom I trust by all my heart.
Mehdi, the greatest brother (in-law) in the world.
And Radvin and Ronika for being my main source of happiness during these years.
Love you.

}
\newcommand{\makededications} {

@@

\vfill
\textbf{Keywords:} galaxies: individual: M31, M101, galaxies: high-redshift, galaxies: star formation, galaxies: stellar content, galaxies: ISM, stars: formation, ISM: clouds, methods: observational, methods: statistical, techniques: image processing
\newpage
\tableofcontents\newpage
\newpage
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures
\newpage
\addcontentsline{toc}{chapter}{List of Tables}
\listoftables\newpage
% \addcontentsline{toc}{chapter}{List of Appendices}
% \listofmyappendices\newpage
%\addcontentsline{toc}{chapter}{List of Abbreviations, Symbols, and Nomenclature}
%\large List of Abbreviations, Symbols, and Nomenclature \normalsize
%\newpage
\end{preliminary}
%% End of the preliminary sections: reset page style and numbering.

### 2016-07-22 version0.0/intro0.01.tex
Submitted version

 %how do you model it? %SED model CIGALE %Population synthesis ----> SFR, stellar mass 
The stellar population synthesis method, which sums stellar spectra to produce a composite spectrum, has been widely utilized since the 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
A thorough SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grain emission such as from polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}.
Many groups have modelled SEDs for different types of galaxies and created SED templates (for more information see the review of \cite{Walcher11} on fitting of SEDs and references therein).
Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs (either by minimizing $\chi^2$ or by Bayesian analysis), using the templates.
One example of an SED-fitting code is {\em CIGALE}: Code Investigating GALaxy Emission~\citep{Noll09}.
It combines SED models and uses Bayesian analysis to find the best-fit SED for observed data in the rest-frame UV-to-IR.
Some of the physical properties of galaxies must be assumed as model input find the best SED, and others are derived from SED-fitting results~\citep[see ][for more detail]{Walcher08}.
For example, the best-fit SED has information regarding star formation history and stellar mass to light ratio.
By integrating star formation history over a specific time scale, SFR can be derived.
Knowing the stellar mass to light ratio, one can use a galaxy's observed luminosity to calculate its stellar mass.

@@

\begin{table}
\caption{Multi-wavelength dust-corrected luminosities, adopted from~\cite{Kennicutt12}}
\label{table3}
\begin{center}
\begin{tabular}{ c c}
\hline\hline
Combined luminosities$^1$ & references\\
\hline
L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 0.46L(TIR)& \cite{Hao11}\\
L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 3.89L(24~$\mu$m)& \cite{Hao11}\\
L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 0.27L(TIR)& \cite{Hao11}\\
L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 2.26L(24~$\mu$m)& \cite{Hao11}\\
L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.0024L(TIR)& \cite{Kennicutt09}\\
L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.020L(24~$\mu$m)& \cite{Kennicutt09}\\
\hline
\end{tabular}
\end{center}
\begin{tablenotes}
\item $^1$ Luminosities are in the form of L($\lambda$) = $\lambda$ L$_{\lambda}$ in erg~s$^{-1}$ 
\end{tablenotes}
\end{table}

>>>>

 %how do you model it? %SED model CIGALE %Population synthesis ----> SFR, stellar mass 
The stellar population synthesis method, which sums stellar spectra to produce a composite spectrum, has been widely utilized since the 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
A thorough SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grain emission such as from polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}.
Many groups have modelled SEDs for different types of galaxies and created SED templates (for more information see the review of \cite{Walcher11} on fitting of SEDs and references therein).
Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs (either by minimizing $\chi^2$ or by Bayesian analysis), using the templates.
One example of an SED-fitting code is {\em CIGALE}: Code Investigating GALaxy Emission~\citep{Noll09}.
It combines SED models and uses Bayesian analysis to find the best-fit SED for observed data in the rest-frame UV-to-IR.
Some of the physical properties of galaxies must be assumed as model input find the best SED, and others are derived from SED-fitting results~\citep[see][for more detail]{Walcher08}.
For example, the best-fit SED has information regarding star formation history and stellar mass to light ratio.
By integrating star formation history over a specific time scale, SFR can be derived.
Knowing the stellar mass to light ratio, one can use a galaxy's observed luminosity to calculate its stellar mass.

@@

\begin{table}
\caption{Multi-wavelength dust-corrected luminosities, adopted from~\cite{Kennicutt12}}
\label{table3}
\begin{center}
\begin{tabular}{ c}
\hline\hline
Combined luminosities$^1$ \\
\hline
L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 0.46L(TIR)$^2$\\
L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 3.89L(24~$\mu$m)$^2$\\
L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 0.27L(TIR)$^2$\\
L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 2.26L(24~$\mu$m)$^2$\\
L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.0024L(TIR)$^3$\\
L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.020L(24~$\mu$m)$^3$\\
\hline
\end{tabular}
\end{center}
\begin{tablenotes}
\item $^1$ Luminosities are in the form of L($\lambda$) = $\lambda$ L$_{\lambda}$ in erg~s$^{-1}$ 
\item $^2$ Calibrated by~\cite{Hao11}
\item $^3$ Calibrated by~\cite{Kennicutt09}
\end{tablenotes}
\end{table}

### 2016-07-22 version0.0/paper1.tex
Submitted version

%P5: How to measure it
A galaxy's metallicity is another physical quantity that likely plays a role in the rate of star formation. However, it affects each component of star formation laws in a different way, making it complicated to fully understand its implications. There are many studies on correlation of metallicity with stellar mass and SFR, as well as the effect of metallicity on the ISM \citep[e.g.][]{Boissier03, Leroy08, Krumholz09, Mannucci10, Dib11a, Lilly13}. These studies suggest that metallicity has a critical role in the formation of H$_2$ gas. Thus there should be a correlation between metallicity and the SFR. \citet{Krumholz09} introduced a theoretical SFR law which suggests that the SFR and metallicity of galaxies have a power-law correlation, but the power-law index changes with the amount of total gas. 
 Using results obtained from both observations and analytical models, \citet{Mannucci10} and \citet{Lilly13} showed that metallicity depends on both stellar mass and the SFR, which they referred to as a 'fundamental metallicity relation'. They found that at any fixed stellar mass, metallicity and the SFR have an inverse correlation. It should be noted that the above two correlations are only valid in the global case. However, \citet{Leroy08} showed that the SFR as measured by combining far-UV and 24$\mu$m emission does not change with changing metallicity. \citet{Roychowdhury15} argued that in nearby spiral galaxies effect of metallicity on the SFR calculation is smaller than the calibration errors and can be ignored. On the other side, \citet{Boissier03} showed that metallicity has an inverse correlation with CO-H$_2$ conversion factor. Therefore, using a constant conversion factor at high metallicity regions causes the overestimation of the molecular gas mass, and in low metallicity it leads to an underestimation.

%P2: SFR, measuring, scaling, ...
In order to investigate star formation laws, the first step is to calculate the SFR. Many studies are devoted to determining how flux measurements of star-forming regions can be accurately translated into the rate of formation of new stars \citep[e.g.][]{Kennicutt12, Calzetti13, Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}. \citet{Kennicutt98b} calibrated luminosity of galaxies as a way of measuring the SFR in specific wavelengths using relations between the SFR per unit mass or per unit luminosity and the integrated colour of the system provided by synthesis models \citep[e.g.][]{Bruzual93}. Subsequent studies tried to find a similar calibration for measuring the SFR of galaxies in other bands. \citet{Kennicutt09} and \citet{Hao11} introduced new SFR calibrations using a combination of \halpha\ or far-ultraviolet (FUV) and far-infrared (FIR) emission. In addition to using suitable calibrations for each region, considering the differences between the global and the local ($\sim 0.5-1$~\kpc) cases is important. In $\S$~\ref{sec:sfr}, we will discuss the SFR in the Andromeda galaxy and how it was determined.

@@

Our first star formation map was produced using a calibration of a combination of FUV emission and 24 \um emission introduced by \citet{Hao11}. Since the peak of the emission of massive and young stars (O-B and A type) is in the UV part of the spectrum, this wavelength is one of the most commonly used star formation rate indicators \citep[e.g.][]{Kennicutt89}. The UV emission traces recently formed stars ($\sim 100$ Myr) \citep[e.g.][]{Kennicutt98a, Calzetti05}. However, the downside of only using the FUV light as a tracer of the star-forming region is that this emission is very sensitive to dust extinction. On the other hand, 24~$\mu$m emission is dominated by emission from dust heated by UV photons from young and hot stars. This emission is sensitive to the star formation timescale of $<10$ Myr \citep{Calzetti07}. The FUV band of \Galex and the 24 \um band of \Spitzer were used to measure the SFR for stars with ages $<100$~Myr calibrated by \citet{Hao11}  using nearby galaxies and the~\citet{Kroupa03} IMF as:
\begin{equation}
\label{equ: fuvplus24}
SFR =4.46\times10^{-44}[L(FUV)_{\mathrm obs}+3.89L(24\mu m)],
\end{equation}
\noindent where SFR is in M$_{\odot}$~yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{\mathrm obs}$ are in erg~s$^{-1}$. L(FUV)$_{\mathrm obs}$ is the luminosity of the galaxy in the FUV. The subscript "obs" indicates that the FUV emission is not corrected for extinction. Nevertheless, this emission was corrected for the foreground stars' emission using a method introduced by \citet{Leroy08}. We masked out pixel values in the FUV$_{obs}$ map for which I$_{NUV}$/I$_{FUV}$ $>$ 15, assuming that those pixels are dominated by foreground emission. This process results in masking about 3 per cent of the pixels within a 25~kpc radius from the centre in the FUV$_{obs}$ map, which leads to a slight underestimate of the total SFR. 
Then we smoothed the FUV$_{obs}$  map to have the same angular resolution and pixel size as the MIPS 24~$\mu$m, and masked the same regions in the 24 \um map as in the FUV$_{obs}$  map. We added all the pixels in the map and calculated the total SFR to be $0.31\pm 0.04$~M$_{\odot}$~yr$^{-1}$. The reported uncertainty for the total SFR only considers the values we measured and does not include uncertainties related to the masked pixels.

@@

The SFR can also be calculated using a combination of \halpha\ and \Spitzer  24 \um maps. \halpha\ emission of galaxies is dominated by light emitted from young and massive stars. Star formation timescales traced by this emission are $\sim 6-10$ Myr \citep[e.g.][]{Kennicutt09, Calzetti13}. Therefore, \halpha\ alone could be used to calibrate the SFR \citep[e.g.][]{Osterbrock06, Kennicutt09}. However, \halpha\ emission is very sensitive to dust extinction. Therefore, the combination of the \halpha\ and 24\um of considered a better choice for calculating the SFR. We used a calibration introduced by \citet{Kennicutt09} to measure the SFR:
\begin{equation}
\label{equ: halphaplus24_g}
SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{\mathrm obs} + 0.020L(24\mu m)],
\end{equation}
\noindent where L(H${\alpha}$)$_{\mathrm obs}$ is the observed \halpha\ luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$. L(24$\mu$m) is the $24\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}~$yr$^{-1}$. It was indicated that the formulation above can only be used for the global situation, i.e., the total SFR.

@@

\begin{table}
\caption{K-S law and Extended Schmidt Law fits for larger pixels}
\label{table:res750}
\begin{adjustbox}{width=\textwidth}
\begin{tabular}{cccccccc}
\hline\hline
\multicolumn{1}{c}{\multirow{1}{*}{Region}}  & Gas Tracer & {\it N} & A  & \nprime & $\beta$ & A$^\prime$ \\
\hline\hline
\multicolumn{1}{c}{\multirow{3}{*}{Whole Galaxy}}
 & H$_2$ only & 0.26 - 0.31 & -10.00 - -9.91  & 0.21 - 0.26  & 0.26 - 0.40    & -10.51 - -10.30  \\
 & H\,{\textsc i} only    & 1.08 - 1.24 & -11.60 - -11.36  & 0.73 - 0.85  & 0.58 - 0.64    & -11.74 - -11.60     \\
 & Total gas  & 0.66 - 0.73 & -10.11 - -10.06 & 0.39 - 0.46    & 0.41 - 0.49    & -11.56 - -10.47     \\
\hline
\multicolumn{1}{c}{\multirow{3}{*}{R$< 8\kpc$}}
 & H$_2$ only & 0.14 - 0.27 & -9.82 - -9.59  & 0.14 - 0.21   & 0.48 - 0.66   & -11.04 - -10.66      \\
 & H\,{\textsc i} only    & 1.42 - 1.68 & -12.35 - -11.92 & 0.51 - 0.92    & 0.72 - 0.97    & -12.52 - -11.61     \\
 & Total gas  & 0.07 - 0.31 & -9.63 - -9.45  & 0.22 - 0.32    & 0.63 - 0.78    & -11.17 - -10.84      \\
\hline
\multicolumn{1}{c}{\multirow{3}{*}{$8\kpc < $R $< 18\kpc$}}
 & H$_2$ only & 0.27 - 0.32 & -9.98 - -9.86  & 0.17 - 0.24    &  0.38 - 0.73   & -10.89 - -10.44       \\
 & H\,{\textsc i} only    & 0.88 - 1.38 & -11.80 - -11.06 & 1.00 - 1.22    & 0.53 - 0.69    & -12.41 - -12.09     \\
 & Total gas  & 0.55 - 0.64 & -10.03 - -9.96 & 0.40 - 0.51    & 0.27 - 0.49    & -10.53 - -10.29     \\
\hline
\multicolumn{1}{c}{\multirow{3}{*}{$18\kpc <$ R $< 25\kpc$}} 
 & H$_2$ only & N/A$^a$& N/A$^a$ & N/A$^a$ &N/A$^a$ & N/A$^a$    \\
 & H\,{\textsc i} only    & 0.46 - 0.81 & -11.21 - -10.80  & 0.44 - 0.76    & 0.13 - 0.36    & -11.35 -10.94     \\
 & Total gas  & 0.47 - 0.82 & -10.25 - -10.18 & 0.44 - 0.78    & 0.12 - 0.36    & -10.49 - -10.30     \\
 \hline
\end{tabular}
\end{adjustbox}
\begin{tablenotes}
\item Similar to Table~\ref{table:res} but here the fitting is performed on regions with a size of 750~pc, and we only show the results from SFR(FUV+24$\mu$m).
\end{tablenotes}
\end{table}

@@

Table~\ref{table:res} shows the results of the hierarchical Bayesian fitting for the whole galaxy and all three regions. Considering the data and uncertainties for each parameter, we are 95 per cent confident that our fitting parameter is in the ranges given in Table~\ref{table:res}.
Our results suggest that changing the gas tracer has a more significant impact on the determination of the power law index than changing the SFR tracers. Therefore, we only discuss the results from SFR(FUV+24$\mu$m), and in Table~\ref{table:res750} we only show results from this SFR map.

>>>>

%P5: How to measure it
A galaxy's metallicity is another physical quantity that likely plays a role in the rate of star formation. However, it affects each component of star formation laws in a different way, making it complicated to fully understand its implications. There are many studies on correlation of metallicity with stellar mass and SFR, as well as the effect of metallicity on the ISM \citep[e.g.][]{Boissier03, Leroy08, Krumholz09, Mannucci10, Dib11a, Dib11b, Lilly13}. These studies suggest that metallicity has a critical role in the formation of H$_2$ gas. Thus there should be a correlation between metallicity and the SFR. \citet{Krumholz09} introduced a theoretical SFR law which suggests that the SFR and metallicity of galaxies have a power-law correlation, but the power-law index changes with the amount of total gas. 
 Using results obtained from both observations and analytical models, \citet{Mannucci10} and \citet{Lilly13} showed that metallicity depends on both stellar mass and the SFR, which they referred to as a 'fundamental metallicity relation'. They found that at any fixed stellar mass, metallicity and the SFR have an inverse correlation. It should be noted that the above two correlations are only valid in the global case. However, \citet{Leroy08} showed that the SFR as measured by combining far-UV and 24~$\mu$m emission does not change with changing metallicity. \citet{Roychowdhury15} argued that in nearby spiral galaxies effect of metallicity on the SFR calculation is smaller than the calibration errors and can be ignored. On the other side, \citet{Boissier03} showed that metallicity has an inverse correlation with CO-H$_2$ conversion factor. Therefore, using a constant conversion factor at high metallicity regions causes the overestimation of the molecular gas mass, and in low metallicity it leads to an underestimation.

%P2: SFR, measuring, scaling, ...
In order to investigate star formation laws, the first step is to calculate the SFR. Many studies are devoted to determining how flux measurements of star-forming regions can be accurately translated into the rate of formation of new stars \citep[e.g.][]{Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11, Kennicutt12, Calzetti13}. \citet{Kennicutt98b} calibrated luminosity of galaxies as a way of measuring the SFR in specific wavelengths using relations between the SFR per unit mass or per unit luminosity and the integrated colour of the system provided by synthesis models \citep[e.g.][]{Bruzual93}. Subsequent studies tried to find a similar calibration for measuring the SFR of galaxies in other bands. \citet{Kennicutt09} and \citet{Hao11} introduced new SFR calibrations using a combination of \halpha\ or far-ultraviolet (FUV) and far-infrared (FIR) emission. In addition to using suitable calibrations for each region, considering the differences between the global and the local ($\sim 0.5-1$~\kpc) cases is important. In $\S$~\ref{sec:sfr}, we will discuss the SFR in the Andromeda galaxy and how it was determined.

@@

Our first star formation map was produced using a calibration of a combination of FUV emission and 24 \um emission introduced by \citet{Hao11}. Since the peak of the emission of massive and young stars (O-B and A type) is in the UV part of the spectrum, this wavelength is one of the most commonly used star formation rate indicators \citep[e.g.][]{Kennicutt89}. The UV emission traces recently formed stars ($\sim 100$ Myr) \citep[e.g.][]{Kennicutt98a, Calzetti05}. However, the downside of only using the FUV light as a tracer of the star-forming region is that this emission is very sensitive to dust extinction. On the other hand, 24~$\mu$m emission is dominated by emission from dust heated by UV photons from young and hot stars. This emission is sensitive to the star formation timescale of $<10$ Myr \citep{Calzetti07}. The FUV band of \Galex and the 24 \um band of \Spitzer were used to measure the SFR for stars with ages $<100$~Myr calibrated by \citet{Hao11}  using nearby galaxies and the~\citet{Kroupa03} IMF as:
\begin{equation}
\label{equ: fuvplus24}
SFR =4.46\times10^{-44}[L(FUV)_{\mathrm obs}+3.89L(24\mu m)],
\end{equation}
\noindent where SFR is in M$_{\odot}$~yr$^{-1}$, and L(24~$\mu$m) and L(FUV)$_{\mathrm obs}$ are in erg~s$^{-1}$. L(FUV)$_{\mathrm obs}$ is the luminosity of the galaxy in the FUV. The subscript "obs" indicates that the FUV emission is not corrected for extinction. Nevertheless, this emission was corrected for the foreground stars' emission using a method introduced by \citet{Leroy08}. We masked out pixel values in the FUV$_{obs}$ map for which I$_{NUV}$/I$_{FUV}$ $>$ 15, assuming that those pixels are dominated by foreground emission. This process results in masking about 3 per cent of the pixels within a 25~kpc radius from the centre in the FUV$_{obs}$ map, which leads to a slight underestimate of the total SFR. 
Then we smoothed the FUV$_{obs}$  map to have the same angular resolution and pixel size as the MIPS 24~$\mu$m, and masked the same regions in the 24 \um map as in the FUV$_{obs}$  map. We added all the pixels in the map and calculated the total SFR to be $0.31\pm 0.04$~M$_{\odot}$~yr$^{-1}$. The reported uncertainty for the total SFR only considers the values we measured and does not include uncertainties related to the masked pixels.

@@

The SFR can also be calculated using a combination of \halpha\ and \Spitzer  24 \um maps. \halpha\ emission of galaxies is dominated by light emitted from young and massive stars. Star formation timescales traced by this emission are $\sim 6-10$ Myr \citep[e.g.][]{Kennicutt09, Calzetti13}. Therefore, \halpha\ alone could be used to calibrate the SFR \citep[e.g.][]{Osterbrock06, Kennicutt09}. However, \halpha\ emission is very sensitive to dust extinction. Therefore, the combination of the \halpha\ and 24\um of considered a better choice for calculating the SFR. We used a calibration introduced by \citet{Kennicutt09} to measure the SFR:
\begin{equation}
\label{equ: halphaplus24_g}
SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{\mathrm obs} + 0.020L(24\mu m)],
\end{equation}
\noindent where L(H${\alpha}$)$_{\mathrm obs}$ is the observed \halpha\ luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$. L(24~$\mu$m) is the $24\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}~$yr$^{-1}$. It was indicated that the formulation above can only be used for the global situation, i.e., the total SFR.

@@

\begin{table}
\caption{K-S law and Extended Schmidt Law fits for larger pixels}
\label{table:res750}
\begin{adjustbox}{width=\textwidth}
\begin{tabular}{cccccccc}
\hline\hline
\multicolumn{1}{c}{\multirow{1}{*}{Region}}  & Gas Tracer & {\it N} & A  & \nprime & $\beta$ & A$^\prime$ \\
\hline\hline
\multicolumn{1}{c}{\multirow{3}{*}{Whole Galaxy}}
 & H$_2$ only & 0.26 - 0.31 & -10.00 - -9.91  & 0.21 - 0.26  & 0.26 - 0.40    & -10.51 - -10.30  \\
 & H\,{\textsc i} only    & 1.08 - 1.24 & -11.60 - -11.36  & 0.73 - 0.85  & 0.58 - 0.64    & -11.74 - -11.60     \\
 & Total gas  & 0.66 - 0.73 & -10.11 - -10.06 & 0.39 - 0.46    & 0.41 - 0.49    & -11.56 - -10.47     \\
\hline
\multicolumn{1}{c}{\multirow{3}{*}{R$< 8\kpc$}}
 & H$_2$ only & 0.14 - 0.27 & -9.82 - -9.59  & 0.14 - 0.21   & 0.48 - 0.66   & -11.04 - -10.66      \\
 & H\,{\textsc i} only    & 1.42 - 1.68 & -12.35 - -11.92 & 0.51 - 0.92    & 0.72 - 0.97    & -12.52 - -11.61     \\
 & Total gas  & 0.07 - 0.31 & -9.63 - -9.45  & 0.22 - 0.32    & 0.63 - 0.78    & -11.17 - -10.84      \\
\hline
\multicolumn{1}{c}{\multirow{3}{*}{$8\kpc < $R $< 18\kpc$}}
 & H$_2$ only & 0.27 - 0.32 & -9.98 - -9.86  & 0.17 - 0.24    &  0.38 - 0.73   & -10.89 - -10.44       \\
 & H\,{\textsc i} only    & 0.88 - 1.38 & -11.80 - -11.06 & 1.00 - 1.22    & 0.53 - 0.69    & -12.41 - -12.09     \\
 & Total gas  & 0.55 - 0.64 & -10.03 - -9.96 & 0.40 - 0.51    & 0.27 - 0.49    & -10.53 - -10.29     \\
\hline
\multicolumn{1}{c}{\multirow{3}{*}{$18\kpc <$ R $< 25\kpc$}} 
 & H$_2$ only & N/A$^a$& N/A$^a$ & N/A$^a$ &N/A$^a$ & N/A$^a$    \\
 & H\,{\textsc i} only    & 0.46 - 0.81 & -11.21 - -10.80  & 0.44 - 0.76    & 0.13 - 0.36    & -11.35 -10.94     \\
 & Total gas  & 0.47 - 0.82 & -10.25 - -10.18 & 0.44 - 0.78    & 0.12 - 0.36    & -10.49 - -10.30     \\
 \hline
\end{tabular}
\end{adjustbox}
\begin{tablenotes}
\item Similar to Table~\ref{table:res} but here the fitting is performed on regions with a size of 750~pc, and we only show the results from SFR(FUV+24~$\mu$m).
\end{tablenotes}
\end{table}

@@

Table~\ref{table:res} shows the results of the hierarchical Bayesian fitting for the whole galaxy and all three regions. Considering the data and uncertainties for each parameter, we are 95 per cent confident that our fitting parameter is in the ranges given in Table~\ref{table:res}.
Our results suggest that changing the gas tracer has a more significant impact on the determination of the power law index than changing the SFR tracers. Therefore, we only discuss the results from SFR(FUV+24~$\mu$m), and in Table~\ref{table:res750} we only show results from this SFR map.
